---
layout: post
title: "This is a test post for my Spotify project"
date: 07-01-2020
tags: test spotify
---

---
title: "Spotify"
output: 
  md_document:
    variant: html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}

#Load the libraries

library(tidyverse)
library(knitr)
library(kableExtra)


setwd("C:/Users/lena/Desktop/Rspace/spot/spot")
```


## Top 50 Tracks in 2019 

An analysis of the top 50 tracks on Spotify with R. **What a way to say goodbye to 2019!** You can find the dataset on Kaggle,  <https://www.kaggle.com/leonardopena/top50spotify2019>.


### Let's take a look at the dataset: ### 
```{r include=FALSE}
top50<-read.csv("top50.csv", sep=",",encoding = "ISO-8859-1")
head(top50, n=10)
```


```{r top50}
summary(top50)
```


```{r popularity_plot}
# Plotting by popularity
top50$Track.Name<-factor(top50$Track.Name,levels=top50$Track.Name[order(top50$Popularity)])

ggplot(top50,aes(x=top50$Track.Name,y=top50$Popularity)) + 
  xlab("Track Name") + 
  ylab("Popularity") + 
  geom_bar(stat="identity") +
  theme(axis.text.x=element_text(angle=90,hjust=1))
```

### What About the Music Genre?

```{r include=FALSE}
# Genre

genre_count<-top50 %>% select(Track.Name,Genre)
genre_count<-genre_count %>% group_by(Genre) %>% summarise(count=n()) %>% arrange(desc(count))

head(genre_count)
```

```{r genre_plot}
# Plotting Genre Count
genre_count$Genre<-factor(genre_count$Genre,levels=genre_count$Genre[order(genre_count$count)])

ggplot(genre_count,aes(x=genre_count$Genre,y=genre_count$count)) + 
  xlab("Genre") + 
  ylab("Count") + 
  geom_bar(stat="identity") +
  theme(axis.text.x=element_text(angle=90,hjust=1))
```

### Artists by Number of Songs in the Top 50 List
```{r include=FALSE}
artist_count<-top50 %>% select(Artist.Name,Track.Name)
artist_count<-artist_count %>% group_by(Artist.Name) %>% summarise(count=n()) %>% arrange(desc(count))
head(artist_count)
```

```{r artist_plot }

knitr::kable(artist_count, col.names = c("Artist","Count")) %>% kable_styling() %>% scroll_box(width="50%",height="200px")

```

### Artists by Popularity of Songs

```{r artist_pop}
artist_pop <-top50 %>% select(Artist.Name,Popularity)
artist_pop <-artist_pop %>% group_by(Artist.Name) %>% summarise(average_pop=mean(Popularity)) %>% arrange(desc(average_pop))

knitr::kable(artist_pop, col.names = c("Artist","Average Popularity")) %>% kable_styling() %>% scroll_box(width="50%",height="200px")

```

### Artists' Energy
```{r artist_char}
artist_energy<-top50 %>% select(Artist.Name,Energy)
artist_energy<-artist_energy %>% group_by(Artist.Name) %>% summarise(average_energy=mean(Energy)) %>% arrange(desc(average_energy))

knitr::kable(artist_energy, col.names = c("Artist","Average Energy")) %>% kable_styling() %>% scroll_box(width="50%",height="200px")

```

### Which Are the Factors Contributing to Popularity?
```{r include=FALSE}
kmeans.data<-top50 %>% select(Beats.Per.Minute,Energy,Loudness..dB..,Valence.,Length.,Acousticness..,Speechiness.,Liveness,Danceability)
kmeans(kmeans.data,centers=18,nstart=20)

```




```{r include=FALSE}
top50.cor<- top50 %>% select(Popularity,Beats.Per.Minute,Energy,Loudness..dB..,Valence.,Length.,Acousticness..,Speechiness.,Liveness,Danceability)

cor(top50.cor)

```
